---
title: "Gapminder analysis"
author: "Andrew Strumpf"
date: "10/14/2019"
output: 
  html_document:
    keep_md: yes
    fig_caption: yes
    toc: yes
---

# Introduction

Here is my first RMarkdown (rmd) document. Because toc is yes any hashtag appears as the table of contents

# Let's embed some R code

First, let's write an R chunk that loads the tidyverse package and then reads in the Gapminder data set from the data subdirectory of the project. 

To create a new R chunk: CTRL + ALT + I

```{r, message=FALSE}
library(tidyverse)
gm <- read.csv("Data/gapminder.csv")

```

# Investigate gm data

What will it show us????

```{r}
head(gm)
```


# Our first plot

Shows gdp per capita on x and life expectancy on y

```{r, fig.cap="Life Expectancy v. GDP"}
ggplot(gm, aes(x = gdpPercap, y = lifeExp)) + geom_point()
```


# A better plot

```{r, fig.cap="Life Expectancy v. GDP w/ color", fig.width=5}
ggplot(gm, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(col = continent)) +
  scale_x_log10()

```

#Alternative chunk options

Options include:
- echo (TRUE by default), etlls whether to include code in the output
- results 
  - hide will hide the reuslts wow!
  - hold will hold results until end of the r chunk
- include (TRUE by default) if FALSE then code will not run aka be evaluated
- fig.width fig.height dimensions of figure in output
- cache (FALSE by default) if TRUE saves result from R chunk

# Table in RMarkdown

Preview the ata using head function

```{r}
head(gm)
```

now head funciton as a nice and neat formatted table


```{r}
library(knitr)
kable(head(gm))
```

If you (me) like tables, look at the **gt** table *package*







